\proglang{collapse}: Advanced and Fast Statistical Computing and Data Transformation in \proglang{R}

### 2025-05-05 misc/JSS article/final/article.Rnw
Resetting global options.

<<preliminaries, echo=FALSE, message=FALSE, warning=FALSE, results=hide>>=
# knitr::opts_chunk$set(cache = FALSE, size = "small")
rm(list = ls()); gc()
options(prompt = "R> ", continue = "+  ", width = 77, digits = 4, useFancyQuotes = FALSE, warn = 1)

@@

# Reset collapse options (if set)
set_collapse(nthreads = 1L, remove = NULL, stable.algo = TRUE, sort = TRUE,
             digits = 2L, stub = TRUE, verbose = 1L, mask = NULL, na.rm = TRUE)

@@

>>>>

<<preliminaries, echo=FALSE, message=FALSE, warning=FALSE, results=hide>>=
# knitr::opts_chunk$set(cache = FALSE, size = "small")
rm(list = ls()); gc()
r_opts <- options(prompt = "R> ", continue = "+  ", width = 77, digits = 4, useFancyQuotes = FALSE, warn = 1)

@@

# Reset collapse options (if set)
oldopts <- set_collapse(nthreads = 1L, remove = NULL, stable.algo = TRUE, sort = TRUE,
             digits = 2L, stub = TRUE, verbose = 1L, mask = NULL, na.rm = TRUE)

@@

<<reset_options, echo=FALSE>>=
options(r_opts)
set_collapse(oldopts)
@
